Improving Software Maintainability through automatic refactoring of Code Clones

### 2019-10-26 saner/paper.tex
Updates from Overleaf

\subsection{Minimum clone size}
% In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, 
When clones are very small, they may never be able to improve maintainability. The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication. We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely\todo{any ref?} to improve maintainability when refactored.

\subsection{Thresholds}
Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile \todo{quartile or quantile?} distribution of empirical data~\cite{alves2010deriving}. 
\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
% Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

@@

\subsection{Calculating a maintainability score}\label{sec:metricformula}
We use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}). We determine the value of each metric before and after for each refactored clone class, resulting in a delta metric score. We aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions derived from supporting evidence~\cite{heitlager2007practical},~\cite{alves2010deriving}:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item Normalizing each metric delta over all deltas obtained for that metric in our dataset results in equally weighted
  scores.\todo{confusing}
  \item \todo{isn't this also an assumption?} all considered metrics do not interfere with the out-of-scope metrics
\end{itemize}

@@

We normalize each obtained metric delta using the ``Standard score''\todo{this name is confusing, is it established? then cite ref, otherwise I don't understand the quotes}, which is calculated as follows \todo{first give the intuition, then the math!}:
\begin{equation}\label{eq:scoredev}
N_{metric} = \frac {\Delta X-\mu}{\sigma}
\end{equation}
Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric. This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively \todo{backup by citing relevant reference}.

@@

\todo[inline]{the paragraph below belongs to discussion}
The results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored. Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.

@@

\subsubsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

>>>>

\subsection{Minimum clone size}
% In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, 
When clones are very small, they may never be able to improve maintainability. The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication. We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely to improve maintainability when refactored (see our results in Sec.~\ref{sec:clonetokenvolume}).

%\subsection{Thresholds}
%Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}. 
%\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
% Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

@@

\subsection{Calculating a maintainability score}\label{sec:metricformula}
We use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}). We determine the value of each metric before and after for each refactored clone class, resulting in a delta metric score. We aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions derived from supporting evidence~\cite{heitlager2007practical},~\cite{alves2010deriving}:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item Normalizing each metric delta over all deltas obtained for that metric in our dataset results in equally weighted
  scores.%\todo{confusing}
  \item All considered metrics do not interfere with the out-of-scope metrics
\end{itemize}

@@

We normalize each obtained metric delta using the standard score, because our data contains many outliers and the standard score is not much affected by those. The standard score is calculated as follows:
\begin{equation}\label{eq:scoredev}
N_{metric} = \frac {\Delta X-\mu}{\sigma}
\end{equation}
Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric. This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.% \todo{backup by citing relevant reference}.

@@

The results show that, given our refactorability criteria, 28\% of clones can be automatically refactored. Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.

@@

\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
